---
title: "The T~50~ App Report"
output: 
 html_document:
   code_folding: show
   toc: true
   toc_float:
     collapsed: false
     smooth_scroll: false
params:
  table: NA
  n_var: NA
  unit: NA
  color_var: NA
  facet_var_row: NA
  facet_var_col: NA
  legend_order: NA
  Bestfit_dataframe: NA
  ScatterPlot_dataframe: NA
  Plot_appearance: NA

---
<style type="text/css">
div.main-container {
  width: 100%;
  max-width: unset;
}

body, td {
   font-size: 18px;
}
code.r{
  font-size: 14px;
}
pre {
  font-size: 14px
}
</style>


This report is used for generating the dose response curves. You can customize the plots by modifying the codes. Just make sure that you have downloaded the dataframes (the excel file) used for plotting.

### Load the required packages
The packages used for plotting are listed below, load these packages before you run the codes.

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(ggplot2)
library(drcte)
library(drc)
library(ggthemes)
library(cowplot)
library(extrafont)
library(ggpubr)
library(writexl)
library(openxlsx)
library(rmarkdown)
```

### T~50~ Tables
The T~50~s estimated by the app are listed below.
```{r echo = FALSE, results='asis'}
kable(params$table, format = "html") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)
```


### Time-to-event Curve
The time-to-event curve is generated by the following codes. You can further customize the plot by modifying the codes. The following items are input variables passed from the app, please change following variables to their corresponding values listed below.  
  
* Variables  
   + `n_var`: `r params$n_var`
   + `unit`: `r params$unit`
   + `color_var`: `r params$color_var`  
   + `facet_var_row`: `r params$facet_var_row`  
   + `facet_var_col`: `r params$facet_var_col`  
   + `legend_order`: `r params$legend_order`  

* Dataframes  
   + `bestfit_dataframe`: dataframe in "**Bestfit_dataframe**"  
   + `scatterplot_dataframe`: dataframe in "**ScatterPlot_dataframe**"  

```{r}
# Passing variables from the app to the report

# Number of variables
n_var <- params$n_var 

# Unit of time
unit <- params$unit

# Variables for assigning line color, row & column of facet plot
color_var <- params$color_var 
facet_var_row <- params$facet_var_row
facet_var_col <- params$facet_var_col

# Legend order
legend_order <- params$legend_order


# Dataframes
bestfit_dataframe <- params$Bestfit_dataframe
scatterplot_dataframe <- params$ScatterPlot_dataframe

# I used the dataframes passing from the app, if you want to use the code you should upload the dataframes stored in the excel file by the following codes
# Remember to add the file path and remove the pound sign before you run the following codes
# bestfit_dataframe <- read.xlsx("ExportedExcel.xlsx", sheet = 2)
# scatterplot_dataframe <- read.xlsx("ExportedExcel.xlsx", sheet = 3)


# Palette
cbPalette = c("#00A4FF", "#FD7FEE", "#03DFCA", "#990A3A", "#F37B63", "#05B756", "#A3FB86", "#097C91", "#015EC9","#840EAA")

# Line plot
if (params$n_var == 0) {
   n_color <- 1
   p <- ggplot(data = bestfit_dataframe, aes(x = After, y = Response)) + 
       scale_color_manual(values = get_palette(cbPalette, n_color))
} else {
   # eval(parse(text = paste0("n_color <- isolate({n_distinct(scatterplot_dataframe$", color_var, ")})")))
   n_color <- n_distinct(scatterplot_dataframe[[color_var]])
   p <- ggplot(data = bestfit_dataframe, aes(x = After, y = Response, color = eval(parse(text = paste0(color_var))), 
                                    group = eval(parse(text = color_var)))) + 
       scale_color_manual(color_var, values = get_palette(cbPalette, n_color), limits = legend_order)
}
# Scatter plot
if (n_var == 0) {
       p <- p + geom_point(data = scatterplot_dataframe, aes(x = After, y = Response), alpha = 0.5)
   } else {
       p <- p + geom_point(data = scatterplot_dataframe, aes(x = After, y = Response, group = eval(parse(text = color_var))), alpha = 0.5)
   }

# Facet_wrap/Facet_grid
if (n_var >= 3) {
    p <- p +
        # facet_grid
        facet_grid(eval(parse(text = paste0(facet_var_row, "~", facet_var_col))))
} else {
    if (n_var > 1){
        p <- p +
            # facet_wrap
            facet_wrap(eval(parse(text = paste0(facet_var_row, "~", facet_var_col))), ncol = 4)
    }
}

# Add other info.
p <- p + 
   geom_line() +
   scale_x_log10() +
   scale_y_continuous(labels = scales::percent) +
   xlab(paste0("Time (", unit, ")")) + 
   ylab("Rate to Event") +
   theme_few() +
   panel_border(colour = "black", size = 1, remove = FALSE) +
   theme(axis.title = element_text(size = 20),
         axis.text = element_text(size = 16),
         strip.text = element_text(size = 18),
         legend.text = element_text(size = 18),
         legend.title = element_text(size = 18))

```

```{r echo = FALSE, out.width = '100%', fig.align = "center"}
p
```

