---
title: "The ED~50~ Estimation Report"
output: 
 html_document:
   code_folding: show
   toc: true
   toc_float:
     collapsed: false
     smooth_scroll: false
params:
  table_mono: NA
  table_rm: NA
  table_stats: NA
  ed50_type: NA
  ed_methods: NA
  two_point_method: NA
  plot_ed50_ck: NA
  plot_lds_m_ck: NA
  plot_resline_ck: NA
  plot_ci_ck: NA
  n_var: NA
  color_var: NA
  facet_var_row: NA
  facet_var_col: NA
  ED_related: NA
  Bestfit_dataframe: NA
  ScatterPlot_dataframe: NA
  Mean_SD_dataframe: NA
  Plot_appearance: NA
  plot_title: NA
  label_x_axis: NA
  label_y_axis: NA
  legend_title: NA
  legend_label: NA
  legend_order: NA
  font_size: NA
  font_family: NA
  palette: NA

---
<style type="text/css">
div.main-container {
  width: 100%;
  max-width: unset;
}

body, td {
   font-size: 18px;
}
code.r{
  font-size: 14px;
}
pre {
  font-size: 14px
}
</style>


This report is used for generating the dose response curves. You can customize the plots by modifying the codes. Just make sure that you have downloaded the dataframes (the excel file) used for plotting.

### Load the required packages
The packages used for plotting are listed below, load these packages before you run the codes.

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(ggplot2)
library(drc)
library(ggthemes)
library(cowplot)
library(extrafont)
library(ggpubr)
library(openxlsx)
library(rmarkdown)
```
```{css, echo = FALSE}
caption {
      color: Black;
      font-size: 1.2em;
    }
```

### Best-Fit Model and Model Assessment
The selected best-fit model and the results of statistical tests are listed below.
```{r echo = FALSE, results='asis'}
# Generate the table with kable and style it with kableExtra
kable(params$table_stats, format = "html") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F, position = "left")

```


### ED~50~ Table
The chosen ED estimation method is `r if (params$ed_methods == 'stdd_method') {paste0("Ritz-Gerhard Method")} else {paste0("Serra-Greco Method")}`. The ED~50~s estimated by the app are listed below. 
```{r message = FALSE, warning = FALSE, echo = FALSE, results = 'asis'}

# Generate the table with kable and style it with kableExtra
df_all <- params$ED_related
n_var <- params$n_var

## ED50 table - Monotonic curves
if (any(df_all$Model %in% c("Log-logistic (4 paras)", "Log-logistic (5 paras)", "Weibull I", "Weibull II"))) {
  kable(params$table_mono, format = "html", caption = "- Monotonic Curves") %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F, position = "left")
}

## ED50 table - Biphasic curves - Low ED50s
if (any(df_all$Model %in% c("Brain-Cousens", "beta", "Cedergreen-Ritz-Streibig"))) {df_bi <- df_all %>% filter(Model %in% c("Brain-Cousens", "beta", "Cedergreen-Ritz-Streibig"))}
if (any(df_all$Model %in% c("Brain-Cousens", "beta", "Cedergreen-Ritz-Streibig"))) {
  if (n_var == 0) {selected_var <- NULL} else {selected_var <- c(1:n_var)}
  bi_low_ed50 <- df_bi[ , c(selected_var, (n_var+12), (n_var+14):(n_var+17))]
  colnames(bi_low_ed50)[(n_var+1):ncol(bi_low_ed50)] <- c("Response at Low ED\u2085\u2080", "Low ED\u2085\u2080 Mean", "Low ED\u2085\u2080 SE", "Low ED\u2085\u2080 Lower Bound", "Low ED\u2085\u2080 Upper Bound")
  bi_low_ed50 <- bi_low_ed50 %>% mutate(across((n_var+1):ncol(bi_low_ed50), ~ map_chr(.x, display_format)))
  kable(bi_low_ed50, format = "html", caption = "- Biphasic Curves (Low ED~50~)") %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F, position = "left")
}

## ED50 table - Biphasic curves - High ED50s
if (any(df_all$Model %in% c("Brain-Cousens", "beta", "Cedergreen-Ritz-Streibig"))) {
  if (n_var == 0) {selected_var <- NULL} else {selected_var <- c(1:n_var)}
  bi_high_ed50 <- df_bi[ , c(selected_var, (n_var+13), (n_var+18):(n_var+21))]
  colnames(bi_high_ed50)[(n_var+1):ncol(bi_high_ed50)] <- c("Response at High ED\u2085\u2080", "High ED\u2085\u2080 Mean", "High ED\u2085\u2080 SE", "High ED\u2085\u2080 Lower Bound", "High ED\u2085\u2080 Upper Bound")
  bi_high_ed50 <- bi_high_ed50 %>% mutate(across((n_var+1):ncol(bi_high_ed50), ~ map_chr(.x, display_format)))
  kable(bi_high_ed50, format = "html", caption = "- Biphasic Curves (High ED~50~)") %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F, position = "left")
}

## ED50 table - Biphasic curves - LDS
if (any(df_all$Model %in% c("Brain-Cousens", "beta", "Cedergreen-Ritz-Streibig"))) {
  if (n_var == 0) {selected_var <- NULL} else {selected_var <- c(1:n_var)}
  bi_lds <- df_bi[ , c(selected_var, (n_var+10), (n_var+22):(n_var+25))]
  colnames(bi_lds)[(n_var+1):ncol(bi_lds)] <- c("Response at LDS", "LDS Mean", "LDS SE", "LDS Lower Bound", "LDS Upper Bound")
  bi_lds <- bi_lds %>% mutate(across((n_var+1):ncol(bi_lds), ~ map_chr(.x, display_format)))
  kable(bi_lds, format = "html", caption = "- Biphasic Curves (LDS)") %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F, position = "left")
}

## ED50 table - Biphasic curves - M
if (any(df_all$Model %in% c("Brain-Cousens", "beta", "Cedergreen-Ritz-Streibig"))) {
  if (n_var == 0) {selected_var <- NULL} else {selected_var <- c(1:n_var)}
  bi_m <- df_bi[ , c(selected_var, (n_var+11), (n_var+26))]
  colnames(bi_m)[(n_var+1):ncol(bi_m)] <- c("Response at M", "M (Maximum Stimulation/Inhibition)")
  bi_m <- bi_m %>% mutate(across((n_var+1):ncol(bi_m), ~ map_chr(.x, display_format)))
  kable(bi_m, format = "html", caption = "- Biphasic Curves (M)") %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F, position = "left")
}

## ED50 table - Biphasic curves - f
if (any(df_all$Model %in% c("Brain-Cousens", "beta", "Cedergreen-Ritz-Streibig"))) {
  if (n_var == 0) {selected_var <- NULL} else {selected_var <- c(1:n_var)}
  bi_f <- df_bi[ , c(selected_var, (n_var+27):(n_var+30))]
  colnames(bi_f)[(n_var+1):ncol(bi_f)] <- c("f", "p-value (f=0)", "f Lower Bound", "f Upper Bound")
  bi_f <- bi_f %>% mutate(across((n_var+1):ncol(bi_f), ~ map_chr(.x, display_format)))
  kable(bi_f, format = "html", caption = "- Biphasic Curves (f)") %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F, position = "left")
}

## Reed-and-Muench method
if (params$ed50_type == "Absolute" & params$two_point_method == TRUE) {
  # Generate the table with kable and style it with kableExtra
  kable(params$table_rm, format = "html", caption = "- Reed-and-Muench Method") %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F, position = "left")
}

```


### Dose Response Curve
The dose response curve is generated by the following codes. You can further customize the plot by modifying the codes. The following items are input variables passed from the app, please change following variables to their corresponding values listed below.  
  
* Variables  
   + `n_var`: `r params$n_var`  
   + `color_var`: `r params$color_var`  
   + `facet_var_row`: `r params$facet_var_row`  
   + `facet_var_col`: `r params$facet_var_col`  
   + `ed50_type`: `r params$ed50_type`  
   + `ed_methods`: `r params$ed_methods`  
   + `plot_ed50_ck`: `r params$plot_ed50_ck`  
   + `plot_lds_m_ck`: `r params$plot_lds_m_ck`  
   + `plot_resline_ck`: `r params$plot_resline_ck`  
   + `plot_ci_ck`: `r params$plot_ci_ck`  
   + `plot_appearance`: `r params$Plot_appearance`  
   + `plot_title`: `r params$plot_title`  
   + `label_x_axis`: `r params$label_x_axis`  
   + `label_y_axis`: `r params$label_y_axis`  
   + `legend_title`: `r params$legend_title`  
   + `legend_label`: `r params$legend_label`  
   + `legend_order`: `r params$legend_order`  
   + `font_size`: `r params$font_size`  
   + `font_family`: `r params$font_family`  
   + `palette`: `r params$palette`  
  
* Dataframes  
   + `ED_related`: dataframe in "**ED_related**"  
   + `bestfit_dataframe`: dataframe in "**Bestfit_dataframe**"  
   + `scatterplot_dataframe`: dataframe in "**ScatterPlot_dataframe**"  
   + `mean_sd_dataframe`: dataframe in "**Mean_SD_dataframe**"  
  
```{r  message = FALSE, warning = FALSE}
# Passing variables from the app to the report

# Number of variables
n_var <- params$n_var 

# Variables for assigning line color, row & column of facet plot
color_var <- params$color_var 
facet_var_row <- params$facet_var_row
facet_var_col <- params$facet_var_col

# ED50-related
ed50_type <- params$ed50_type
ed_methods <- params$ed_methods

# Show the ED-related lines
plot_ed50_ck <- params$plot_ed50_ck
plot_lds_m_ck <- params$plot_lds_m_ck
plot_resline_ck <- params$plot_resline_ck
plot_ci_ck <- params$plot_ci_ck

# The appearance of plot - plot with all replications or mean & sd
plot_appearance <- params$Plot_appearance

# Dataframes
ED_related <- params$ED_related
bestfit_dataframe <- params$Bestfit_dataframe
scatterplot_dataframe <- params$ScatterPlot_dataframe
mean_sd_dataframe <- params$Mean_SD_dataframe

# Parameters for customized plot
# Label
plot_title <- params$plot_title
label_x_axis <- params$label_x_axis
label_y_axis <- params$label_y_axis
# Legend
legend_title <- params$legend_title
legend_label <- unlist(strsplit(params$legend_label, ", "))
legend_order <- unlist(strsplit(params$legend_order, ", "))
# Font_related
font_size <- as.numeric(params$font_size)
font_family <- params$font_family
# Line_related
palette <- unlist(strsplit(params$palette, ", "))

# I used the dataframes passing from the app, if you want to use the code you should upload the dataframes stored in the excel file by the following codes
# Remember to add the file path and remove the pound sign before you run the following codes
# ED_related <- read.xlsx("ExportedExcel.xlsx", sheet = 1)
# bestfit_dataframe <- read.xlsx("ExportedExcel.xlsx", sheet = 2)
# scatterplot_dataframe <- read.xlsx("ExportedExcel.xlsx", sheet = 3)
# mean_sd_dataframe <- read.xlsx("ExportedExcel.xlsx", sheet = 4)

# Annotation dataframe
ED_related[, (n_var+8):ncol(ED_related)] <- lapply(ED_related[, (n_var+8):ncol(ED_related)], as.numeric)
colnames(ED_related)[(n_var+8):(n_var+26)] <- c("Maximum_Response", "Minimum_Response", "Start_Response", "M_Response", "Response_at_Low_ED50", "Response_at_High_ED50",
                                                "Low_ED50_Mean", "Low_ED50_SE", "Low_ED50_LowerBound", "Low_ED50_UpperBound", 
                                                "High_ED50_Mean", "High_ED50_SE", "High_ED50_LowerBound", "High_ED50_UpperBound",
                                                "LDS_Mean", "LDS_SE", "LDS_LowerBound", "LDS_UpperBound", "M")

if (n_var == 0) {
  # color
  clr <- palette
  # plot
  p <- ggplot(data = bestfit_dataframe, aes(x = Conc, y = Response)) + geom_line(color = clr)
  # appearance
  if (plot_appearance == "all") {
    p <- p + geom_point(data = scatterplot_dataframe, aes(x = Conc, y = Response), alpha = 0.5, color = clr)
  } else {
    p <- p + geom_point(data = mean_sd_dataframe, aes(x = Conc, y = Mean), alpha = 0.5, color = clr) + 
      geom_errorbar(data = mean_sd_dataframe, aes(x = Conc, y = Mean, ymin = Mean - SD, ymax = Mean + SD), width = 0.2, alpha = 0.8, color = clr)
  }
  # ED50
  if (plot_ed50_ck == TRUE) {
    p <- p + 
      # response lines
      geom_hline(data = ED_related, aes(yintercept = Response_at_Low_ED50), linetype = "longdash", alpha = 0.5, color = clr) + 
      geom_hline(data = ED_related, aes(yintercept = Response_at_High_ED50), linetype = "longdash", alpha = 0.5, color = clr) + 
      # ed lines - left
      geom_vline(data = ED_related, aes(xintercept = Low_ED50_Mean), linetype = "longdash", alpha = 0.5, color = clr) + 
      # ed lines - right
      geom_vline(data = ED_related, aes(xintercept = High_ED50_Mean), linetype = "longdash", alpha = 0.5, color = clr)
    
    if (plot_ci_ck == TRUE) {
        p <- p + 
          # ed lines - left
          geom_vline(data = ED_related, aes(xintercept = Low_ED50_LowerBound), linetype = "dotted", alpha = 0.5, color = clr) + 
          geom_vline(data = ED_related, aes(xintercept = Low_ED50_UpperBound), linetype = "dotted", alpha = 0.5, color = clr) +
          # ed lines - right
          geom_vline(data = ED_related, aes(xintercept = High_ED50_LowerBound), linetype = "dotted", alpha = 0.5, color = clr) + 
          geom_vline(data = ED_related, aes(xintercept = High_ED50_UpperBound), linetype = "dotted", alpha = 0.5, color = clr)
      }
  }
  # Max & Min
    if (plot_resline_ck == TRUE) {
      p <- p +
        # response lines
        geom_hline(data = ED_related, aes(yintercept = Maximum_Response), linetype = "longdash", alpha = 0.5, color = clr) + 
        geom_hline(data = ED_related, aes(yintercept = Minimum_Response), linetype = "longdash", alpha = 0.5, color = clr)
    }
    # LDS & M
    if (any(ED_related$Model %in% c("Brain-Cousens", "beta", "Cedergreen-Ritz-Streibig"))) {
      if (plot_lds_m_ck == TRUE) {
        p <- p +
          # LDS
          geom_hline(data = ED_related, aes(yintercept = Start_Response), linetype = "longdash", alpha = 0.5, color = clr) + 
          geom_vline(data = ED_related, aes(xintercept = LDS_Mean), linetype = "longdash", alpha = 0.5, color = clr) + 
          # M
          geom_hline(data = ED_related, aes(yintercept = M_Response), linetype = "longdash", alpha = 0.5, color = clr) + 
          geom_vline(data = ED_related, aes(xintercept = M), linetype = "longdash", alpha = 0.5, color = clr)
        
        if (plot_ci_ck == TRUE) {
          p <- p +
            # LDS
            geom_vline(data = ED_related, aes(xintercept = LDS_LowerBound), linetype = "dotted", alpha = 0.5, color = clr) + 
            geom_vline(data = ED_related, aes(xintercept = LDS_UpperBound), linetype = "dotted", alpha = 0.5, color = clr)
        }
      }
    }
  
} else {
  # plot
  p <- ggplot(data = bestfit_dataframe, aes(x = Conc, y = Response, color = eval(parse(text = color_var)), 
                                        group = eval(parse(text = color_var)))) + 
    geom_line() + 
    scale_color_manual(values = palette, name = legend_title, 
                       limits = legend_order, labels = legend_label)
  # appearance
  if (plot_appearance == "all") {
    p <- p + geom_point(data = scatterplot_dataframe, aes(x = Conc, y = Response, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), alpha = 0.5)
  } else {
    p <- p + 
      geom_point(data = mean_sd_dataframe, aes(x = Conc, y = Mean, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), alpha = 0.5) + 
      geom_errorbar(data = mean_sd_dataframe, aes(x = Conc, y = Mean, group = eval(parse(text = color_var)), color = eval(parse(text = color_var)), 
                                                  ymin = Mean - SD, ymax = Mean + SD), width = 0.2, alpha = 0.8)
  }
  # ED50
  if (plot_ed50_ck == TRUE) {
    p <- p + 
      # response lines
      geom_hline(data = ED_related, aes(yintercept = Response_at_Low_ED50, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "longdash", alpha = 0.5) + 
      geom_hline(data = ED_related, aes(yintercept = Response_at_High_ED50, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "longdash", alpha = 0.5) + 
      # ed lines - left
      geom_vline(data = ED_related, aes(xintercept = Low_ED50_Mean, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "longdash", alpha = 0.5) + 
      # ed lines - right
      geom_vline(data = ED_related, aes(xintercept = High_ED50_Mean, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "longdash", alpha = 0.5)
    
    if (plot_ci_ck == TRUE) {
        p <- p + 
          # ed lines - left
          geom_vline(data = ED_related, aes(xintercept = Low_ED50_LowerBound, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "dotted", alpha = 0.5) + 
          geom_vline(data = ED_related, aes(xintercept = Low_ED50_UpperBound, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "dotted", alpha = 0.5) +
          # ed lines - right
          geom_vline(data = ED_related, aes(xintercept = High_ED50_LowerBound, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "dotted", alpha = 0.5) + 
          geom_vline(data = ED_related, aes(xintercept = High_ED50_UpperBound, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "dotted", alpha = 0.5)
      }
  }
  # Max & Min
  if (plot_resline_ck == TRUE) {
    p <- p +
      # response lines
      geom_hline(data = ED_related, aes(yintercept = Maximum_Response, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "longdash", alpha = 0.5) + 
      geom_hline(data = ED_related, aes(yintercept = Minimum_Response, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "longdash", alpha = 0.5)
  }
  # LDS & M
  if (any(ED_related$Model %in% c("Brain-Cousens", "beta", "Cedergreen-Ritz-Streibig"))) {
    if (plot_lds_m_ck == TRUE) {
      p <- p +
        # LDS
        geom_hline(data = ED_related, aes(yintercept = Start_Response, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "longdash", alpha = 0.5) + 
        geom_vline(data = ED_related, aes(xintercept = LDS_Mean, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "longdash", alpha = 0.5) +
        # M
        geom_hline(data = ED_related, aes(yintercept = M_Response, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "longdash", alpha = 0.5) + 
        geom_vline(data = ED_related, aes(xintercept = M, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "longdash", alpha = 0.5)
      
      if(plot_ci_ck == TRUE) {
        p <- p +
          # LDS
          geom_vline(data = ED_related, aes(xintercept = LDS_LowerBound, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "dotted", alpha = 0.5) + 
          geom_vline(data = ED_related, aes(xintercept = LDS_UpperBound, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "dotted", alpha = 0.5)
      }
    }
  }
}

# Facet_wrap/Facet_grid
if (n_var >= 3) {
    p <- p +
        # facet_grid
        facet_grid(eval(parse(text = paste0(facet_var_row, "~", facet_var_col))))
} else {
    if (n_var > 1){
        p <- p +
            # facet_wrap
            facet_wrap(eval(parse(text = paste0(facet_var_row, "~", facet_var_col))), ncol = 4)
    }
}

# Add other info.
p_cus <- p + 
  scale_x_log10() +
  xlab(label_x_axis) +  
  ylab(label_y_axis) + 
  ggtitle(plot_title) + 
  theme_few() + 
  panel_border(colour = "black", size = 1, remove = FALSE) + 
  theme(axis.title = element_text(size = font_size + 2),
        plot.title = element_text(hjust = 0.5, size = font_size + 4), 
        axis.text = element_text(size = font_size),
        strip.text = element_text(size = font_size + 2),
        legend.text = element_text(size = font_size),
        legend.title = element_text(size = font_size + 2),
        text = element_text(family = font_family))



```

```{r message = FALSE, warning = FALSE, echo = FALSE, out.width = '100%', fig.align = "center"}
p_cus
```

