---
title: "The ED~50~ Estimation Report"
output: 
 html_document:
   code_folding: show
   toc: true
   toc_float:
     collapsed: false
     smooth_scroll: false
params:
  table_ed50: NA
  table_rm: NA
  table_stats: NA
  ed50_type: NA
  ed_methods: NA
  two_point_method: NA
  plot_ed50_ck: NA
  n_var: NA
  color_var: NA
  facet_var_row: NA
  facet_var_col: NA
  legend_order: NA
  ED_related: NA
  Bestfit_dataframe: NA
  ScatterPlot_dataframe: NA
  Mean_SD_dataframe: NA
  Plot_appearance: NA
  label_x_axis: NA
  label_y_axis: NA

---
<style type="text/css">
div.main-container {
  width: 100%;
  max-width: unset;
}

body, td {
   font-size: 18px;
}
code.r{
  font-size: 14px;
}
pre {
  font-size: 14px
}
</style>


This report is used for generating the dose response curves. You can customize the plots by modifying the codes. Just make sure that you have downloaded the dataframes (the excel file) used for plotting.

### Load the required packages
The packages used for plotting are listed below, load these packages before you run the codes.

```{r message = FALSE, warning = FALSE}
library(tidyverse)
library(ggplot2)
library(drc)
library(ggthemes)
library(cowplot)
library(extrafont)
library(ggpubr)
library(openxlsx)
library(rmarkdown)
```
```{css, echo = FALSE}
caption {
      color: Black;
      font-size: 1.2em;
    }
```

### Best-Fit Model and Model Assessment
The selected best-fit model and the results of statistical tests are listed below.
```{r echo = FALSE, results='asis'}
# Generate the table with kable and style it with kableExtra
kable(params$table_stats, format = "html") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F, position = "left")

```


### ED~50~ Table
The chosen ED estimation method is `r if (params$ed_methods == 'stdd_method') {paste0("Ritz-Gerhard Method")} else {paste0("Serra-Greco Method")}`. The ED~50~s estimated by the app are listed below. 
```{r echo = FALSE, results='asis'}

# Generate the table with kable and style it with kableExtra
## ED50 table
kable(params$table_ed50, format = "html", caption = "ED~50~ Estimation Table") %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F, position = "left")
if (params$ed50_type == "Absolute" & params$two_point_method == TRUE) {
  # Generate the table with kable and style it with kableExtra
  kable(params$table_rm, format = "html", caption = "ED~50~ Estimation Table - Reed-and-Muench Method") %>% 
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F, position = "left")
}


```


### Dose Response Curve
The dose response curve is generated by the following codes. You can further customize the plot by modifying the codes. The following items are input variables passed from the app, please change following variables to their corresponding values listed below.  
  
* Variables  
   + `n_var`: `r params$n_var`
   + `color_var`: `r params$color_var`  
   + `facet_var_row`: `r params$facet_var_row`  
   + `facet_var_col`: `r params$facet_var_col`  
   + `ed50_type`: `r params$ed50_type`  
   + `ed_methods`: `r params$ed_methods`  
   + `plot_ed50_ck`: `r params$plot_ed50_ck`  
   + `legend_order`: `r params$legend_order`  
   + `plot_appearance`: `r params$Plot_appearance`  
   + `label_x_axis`: `r params$label_x_axis`  
   + `label_y_axis`: `r params$label_y_axis`  
  
* Dataframes  
   + `ED_related`: dataframe in "**ED_related**"  
   + `bestfit_dataframe`: dataframe in "**Bestfit_dataframe**"  
   + `scatterplot_dataframe`: dataframe in "**ScatterPlot_dataframe**"  
   + `mean_sd_dataframe`: dataframe in "**Mean_SD_dataframe**"  
  
```{r}
# Passing variables from the app to the report

# Number of variables
n_var <- params$n_var 

# Variables for assigning line color, row & column of facet plot
color_var <- params$color_var 
facet_var_row <- params$facet_var_row
facet_var_col <- params$facet_var_col

# ED50-related
ed50_type <- params$ed50_type
ed_methods <- params$ed_methods

# Show the ED-related lines
plot_ed50_ck <- params$plot_ed50_ck

# Legend order
legend_order <- params$legend_order

# The appearance of plot - plot with all replications or mean & sd
plot_appearance <- params$Plot_appearance

# The label for both axises
label_x_axis <- params$label_x_axis
label_y_axis <- params$label_y_axis

# Dataframes
ED_related <- params$ED_related
bestfit_dataframe <- params$Bestfit_dataframe
scatterplot_dataframe <- params$ScatterPlot_dataframe
mean_sd_dataframe <- params$Mean_SD_dataframe

# I used the dataframes passing from the app, if you want to use the code you should upload the dataframes stored in the excel file by the following codes
# Remember to add the file path and remove the pound sign before you run the following codes
# ED_related <- read.xlsx("ExportedExcel.xlsx", sheet = 1)
# bestfit_dataframe <- read.xlsx("ExportedExcel.xlsx", sheet = 2)
# scatterplot_dataframe <- read.xlsx("ExportedExcel.xlsx", sheet = 3)
# mean_sd_dataframe <- read.xlsx("ExportedExcel.xlsx", sheet = 4)

# Palette
cbPalette <- c("#00A4FF", "#FD7FEE", "#03DFCA", "#990A3A", "#F37B63", "#05B756", "#A3FB86", "#097C91", "#015EC9","#840EAA")

# Annotation dataframe
ED_related[, (n_var+7):ncol(ED_related)] <- lapply(ED_related[, (n_var+7):ncol(ED_related)], as.numeric)


if (n_var == 0) {
  # color
  clr <- get_palette(cbPalette, 1)
  # plot
  p <- ggplot(data = bestfit_dataframe, aes(x = Conc, y = Response)) + geom_line(color = clr)
  # appearance
  if (plot_appearance == "all") {
    p <- p + geom_point(data = scatterplot_dataframe, aes(x = Conc, y = Response), alpha = 0.5, color = clr)
  } else {
    p <- p + geom_point(data = mean_sd_dataframe, aes(x = Conc, y = Mean), alpha = 0.5, color = clr) + 
      geom_errorbar(data = mean_sd_dataframe, aes(x = Conc, y = Mean, ymin = Mean - SD, ymax = Mean + SD), width = 0.2, alpha = 0.8, color = clr)
  }
  # ED50
  if (plot_ed50_ck == TRUE) {
    if (ed_methods == 'serra_greco_method') {
      if (any(c("Brain-Cousens", "beta") %in% ED_related$Model)) {
        p <- p +
          # response lines
          geom_hline(data = ED_related, aes(yintercept = SG_Response_at_ED50), linetype = "longdash", alpha = 0.5, color = clr) + 
          # ed lines - left
          geom_vline(data = ED_related, aes(xintercept = SG_Low_ED50_Mean), linetype = "longdash", alpha = 0.5, color = clr) + 
          geom_vline(data = ED_related, aes(xintercept = SG_Low_ED50_LowerBound), linetype = "dotted", alpha = 0.5, color = clr) + 
          geom_vline(data = ED_related, aes(xintercept = SG_Low_ED50_UpperBound), linetype = "dotted", alpha = 0.5, color = clr) +
          # ed lines - right
          geom_vline(data = ED_related, aes(xintercept = SG_High_ED50_Mean), linetype = "longdash", alpha = 0.5, color = clr) + 
          geom_vline(data = ED_related, aes(xintercept = SG_High_ED50_LowerBound), linetype = "dotted", alpha = 0.5, color = clr) + 
          geom_vline(data = ED_related, aes(xintercept = SG_High_ED50_UpperBound), linetype = "dotted", alpha = 0.5, color = clr)
      } else {
        p <- p + 
          # response lines
          geom_hline(data = ED_related, aes(yintercept = SG_Response_at_ED50), linetype = "longdash", alpha = 0.5, color = clr) + 
          # ed lines - left
          geom_vline(data = ED_related, aes(xintercept = SG_ED50_Mean), linetype = "longdash", alpha = 0.5, color = clr) + 
          geom_vline(data = ED_related, aes(xintercept = SG_ED50_LowerBound), linetype = "dotted", alpha = 0.5, color = clr) + 
          geom_vline(data = ED_related, aes(xintercept = SG_ED50_UpperBound), linetype = "dotted", alpha = 0.5, color = clr)
      }
    } else {
      p <- p +
        # response lines
        geom_hline(data = ED_related, aes(yintercept = RG_Response_at_ED50), linetype = "longdash", alpha = 0.5, color = clr) + 
        # ed lines
        geom_vline(data = ED_related, aes(xintercept = RG_ED50_Mean), linetype = "longdash", alpha = 0.5, color = clr) + 
        geom_vline(data = ED_related, aes(xintercept = RG_ED50_LowerBound), linetype = "dotted", alpha = 0.5, color = clr) + 
        geom_vline(data = ED_related, aes(xintercept = RG_ED50_UpperBound), linetype = "dotted", alpha = 0.5, color = clr)
    }
  }
  
 } else {
  # color
  n_color <- isolate({n_distinct(scatterplot_dataframe[[color_var]])})
  # plot
  p <- ggplot(data = bestfit_dataframe, aes(x = Conc, y = Response, color = eval(parse(text = color_var)), 
                                        group = eval(parse(text = color_var)))) + 
    geom_line() + 
    scale_color_manual(color_var, values = get_palette(cbPalette, n_color), limits = legend_order)
  # appearance
  if (plot_appearance == "all") {
    p <- p + geom_point(data = scatterplot_dataframe, aes(x = Conc, y = Response, group = eval(parse(text = color_var))), alpha = 0.5)
  } else {
    p <- p + geom_point(data = mean_sd_dataframe, aes(x = Conc, y = Mean, group = eval(parse(text = color_var))), alpha = 0.5) + 
      geom_errorbar(data = mean_sd_dataframe, aes(x = Conc, y = Mean, group = eval(parse(text = color_var)),
                                                       ymin = Mean - SD, ymax = Mean + SD), width = 0.2, alpha = 0.8)
  }
  # ED50
  if (plot_ed50_ck == TRUE) {
    if (ed_methods == 'serra_greco_method') {
      if (any(c("Brain-Cousens", "beta") %in% ED_related$Model)) {
        p <- p + 
          # response lines
          geom_hline(data = ED_related, aes(yintercept = SG_Response_at_ED50, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "longdash", alpha = 0.5) + 
          # ed lines - left
          geom_vline(data = ED_related, aes(xintercept = SG_Low_ED50_Mean, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "longdash", alpha = 0.5) + 
          geom_vline(data = ED_related, aes(xintercept = SG_Low_ED50_LowerBound, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "dotted", alpha = 0.5) + 
          geom_vline(data = ED_related, aes(xintercept = SG_Low_ED50_UpperBound, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "dotted", alpha = 0.5) +
          # ed lines - right
          geom_vline(data = ED_related, aes(xintercept = SG_High_ED50_Mean, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "longdash", alpha = 0.5) + 
          geom_vline(data = ED_related, aes(xintercept = SG_High_ED50_LowerBound, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "dotted", alpha = 0.5) + 
          geom_vline(data = ED_related, aes(xintercept = SG_High_ED50_UpperBound, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "dotted", alpha = 0.5)
      } else {
        p <- p + 
          # response lines
          geom_hline(data = ED_related, aes(yintercept = SG_Response_at_ED50, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "longdash", alpha = 0.5) + 
          # ed lines - left
          geom_vline(data = ED_related, aes(xintercept = SG_ED50_Mean, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "longdash", alpha = 0.5) + 
          geom_vline(data = ED_related, aes(xintercept = SG_ED50_LowerBound, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "dotted", alpha = 0.5) + 
          geom_vline(data = ED_related, aes(xintercept = SG_ED50_UpperBound, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "dotted", alpha = 0.5)
      }
    } else {
      p <- p +
        # response lines
        geom_hline(data = ED_related, aes(yintercept = RG_Response_at_ED50, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "longdash", alpha = 0.5) + 
        # ed lines
        geom_vline(data = ED_related, aes(xintercept = RG_ED50_Mean, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "longdash", alpha = 0.5) + 
        geom_vline(data = ED_related, aes(xintercept = RG_ED50_LowerBound, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "dotted", alpha = 0.5) + 
        geom_vline(data = ED_related, aes(xintercept = RG_ED50_UpperBound, group = eval(parse(text = color_var)), color = eval(parse(text = color_var))), linetype = "dotted", alpha = 0.5)
    }
  }
}

# Facet_wrap/Facet_grid
if (n_var >= 3) {
    p <- p +
        # facet_grid
        facet_grid(eval(parse(text = paste0(facet_var_row, "~", facet_var_col))))
} else {
    if (n_var > 1){
        p <- p +
            # facet_wrap
            facet_wrap(eval(parse(text = paste0(facet_var_row, "~", facet_var_col))), ncol = 4)
    }
}

# Add other info.
p <- p + 
   scale_x_log10() +
   xlab(label_x_axis) + 
   ylab(label_y_axis) +
   theme_few() +
   panel_border(colour = "black", size = 1, remove = FALSE) +
   theme(axis.title = element_text(size = 20),
         axis.text = element_text(size = 16),
         strip.text = element_text(size = 18),
         legend.text = element_text(size = 18),
         legend.title = element_text(size = 18))

```

```{r echo = FALSE, out.width = '100%', fig.align = "center"}
p
```

